### 2025-07-07 index.qmd
20250705 - message = NA
20250706 - track chunk execution times attempt 1

```{r setup}
#| include: false

# Enable automatic chunk timing logging to GitHub Actions
knitr::opts_chunk$set(time = TRUE)  # Apply to ALL chunks globally

@@

# Define timing hook
knitr::knit_hooks$set(time = function(before, options) {
  if (before) {
    options$start_time <- Sys.time()
  } else {
    elapsed <- difftime(Sys.time(), options$start_time, units = "secs")
    msg <- sprintf("::notice title=Chunk Time::Chunk `%s` ran in %.2f seconds.", 
                   options$label %||% "<unnamed>", as.numeric(elapsed))
    message(msg)  # Send to GitHub Actions log
  }
})
```

>>>>

```{r}
#| label: setup
#| include: false

# Global knitr options
knitr::opts_chunk$set(
  time = TRUE,
  message = NA # Show in console, not in rendered output
)

@@

# Log file setup
log_file <- "chunk-times.txt"
if (file.exists(log_file)) file.remove(log_file)

# Environment to track start times
.chunk_times_env <- new.env()

# Timing hook
knitr::knit_hooks$set(time = function(before, options) {
  label <- options$label %||% "<unnamed>"

  if (before) {
    .chunk_times_env[[label]] <- Sys.time()
  } else {
    start_time <- .chunk_times_env[[label]]
    if (!is.null(start_time)) {
      elapsed <- difftime(Sys.time(), start_time, units = "secs")
      msg <- sprintf("Chunk `%s` ran in %.2f seconds.", label, as.numeric(elapsed))

      # Send message to GitHub Actions log
      message(sprintf("::notice title=Chunk Time::%s", msg))

      # Also save to file
      cat(msg, file = log_file, append = TRUE, sep = "\n")
    }
  }
})
```
